Reduced plasticity and opportunity for selection in terrestrial ectotherm populations under climate change

### 2023-03-28 ms.qmd
Update to ref
Re-render and starting to write last section
Fixed colour scheme pub bias.

Temperature data was extracted using the monthly averages provided by the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx]. For each population and species in the dataset we extracted a 30-year period (1958-2022) of either surface temperature at 2 meters for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa using the *ncdf4* R package [vers. `r utils::packageVersion("ncdf4")`, @Pierce2021]. We chose a 2-meter resolution because we believed that it more likely to reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.

@@

    slope_f <-     posteriors[,"b_cv_c"]; pmcmc(slope_f); quantile(slope_f, c(0.025, 0.975))
    slope_m <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatm"]; pmcmc(slope_m); quantile(slope_m, c(0.025, 0.975))
    slope_t <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatt"]; pmcmc(slope_t); quantile(slope_t, c(0.025, 0.975))

@@

    model3.9_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_t)
        # Model just quickly tests if we are missing an important interaction. It may not necessarily be just about the variability. We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things. We want predictability AND variance
    model3.10_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_t)
    # Freshwater Models
    model3.8_f  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_f)

@@

@@

```{r}
#| label: fig-figs2
#| fig-cap: Funnel plot of precision (1/sampling standard error) against effect size for A) log response ratio $Q_{10}$ ($lnRR_{Q_{10}}$), B)log coefficient of variance ratio $Q_{10}$ ($lnCVR_{Q_{10}}$) and C) log variance ratio $Q_{10}$ ($lnVR_{Q_{10}}$). Both acute ('green') and acclimation ('orange') effect sizes are plotted.
cols <- c("#2ECC71", "#FFC300")
ps2_1 <- ggplot(lnRRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnRR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15), legend.position = "none") + scale_color_manual(name = "Type", values = cols)

>>>>

Temperature data was extracted using the monthly averages provided by the ERA5 climate model, available from the Copernicus climate data store [@Hersbach2020-hx]. For each population and species in the dataset we extracted a 30-year period (1958-2022) of either surface temperature at 2 meters for both terrestrial and freshwater taxa, or sea surface temperature for the marine taxa using the *ncdf4* R package [vers. `r utils::packageVersion("ncdf4")`, @Pierce2021-lc]. We chose a 2-meter resolution because we believed that it more likely to reflects the micro-thermal environment experienced by terrestrial and freshwater ectotherms at those locations.

@@

    slope_f <-     posteriors[,"b_cv_c"]; pmcmc(slope_f); mean(slope_f); quantile(slope_f, c(0.025, 0.975))
    slope_m <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatm"]; pmcmc(slope_m); quantile(slope_m, c(0.025, 0.975))
    slope_t <-     posteriors[,"b_cv_c"] + posteriors[,"b_cv_c:habitatt"]; pmcmc(slope_t); quantile(slope_t, c(0.025, 0.975))

@@

    model3.9_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_t)

       r2_t <- r2_ml(model3.9_t)[1]                       
        # Model just quickly tests if we are missing an important interaction. It may not necessarily be just about the variability. We could have variable sites, but a variance site that has some predictability vs a variable site without predictability are two different things. We want predictability AND variance
    model3.10_t  <- metafor::rma.mv(effect_size ~ c_accl_time + cv_c + acf_all_c + acf_all_c:cv_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_t)
    # Freshwater Models
    model3.8_f  <- metafor::rma.mv(effect_size ~ c_accl_time + acf_all_c, V = V,
                                       random = list(~1 | record_num,
                                            ~1 | species_full,
                                            ~1 | trait,
                                            ~1 | spp,
                                            ~1 | obs),
                              R = list(species_full = phylo_cor_wild_acclim), dfs = "contain", 
                              test = "t", data = lnRRQ10_data_wild_acclim_f)

@@

Thermal variability (i.e., $CV$) explained acclimation capacity among terrestrial ectotherms, but explained little variability in acclimation responses among marine or freshwater populations (@fig-fig8). Wild populations with a history of greater thermal variability were more likely to show greater capacity for thermal acclimation compared to populations with lower thermal variability (`r mean(slope_t)`, 95%CI: `r quantile(slope_t, 0.025)[1]` to `r quantile(slope_t, 0.975)[1]`, $p_{mcmc}$ = `r pmcmc(slope_t)`; $R^2$ = `r r2_t*100`%). In contrast, thermal predcitability did not explain much variation across marine, freshwater or terrestrial ectotherm populations (@fig-fig8).

@@

```{r}
#| label: fig-figs2
#| fig-cap: Funnel plot of precision (1/sampling standard error) against effect size for A) log response ratio $Q_{10}$ ($lnRR_{Q_{10}}$), B)log coefficient of variance ratio $Q_{10}$ ($lnCVR_{Q_{10}}$) and C) log variance ratio $Q_{10}$ ($lnVR_{Q_{10}}$). Both acute ('green') and acclimation ('orange') effect sizes are plotted.
cols <- c("#303234", "#D3D3D3")
ps2_1 <- ggplot(lnRRQ10_data, aes(y = 1/sqrt(V), x = effect_size, color = type)) + geom_point() + theme_classic() + labs(y = TeX("Precision\\ $\\left( \\frac{1}{\\sqrt{V}} \\right)$"), x = TeX("$lnRR_{Q_{10}}$"))+geom_vline(xintercept = 0, linetype = 3) + theme(legend.title  = element_text(size = 15), legend.text = element_text(size = 15), axis.title = element_text(size = 15), axis.text = element_text(size = 15), legend.position = "none") + scale_color_manual(name = "Type", values = cols)
